CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to Support Active Travel}

### 2023-10-03 paper.tex
Update with route network type figures

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, sharp corners, boxrule=0pt, enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

@@

{\centering \includegraphics{images/paste-5.png}

@@

\caption{`Fastest' route network for Limerick}

{\centering \includegraphics{images/paste-6.png}

@@

\caption{`Quietest' route network for Limerick}

@@

\caption{\label{fig-route-types}Illustration of the `Fastest' and
`Quietest' route networks for central and East Limmerick.}

>>>>

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, interior hidden, enhanced, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

\begin{minipage}[t]{\linewidth}

@@

\raisebox{-\height}{

\includegraphics{images/paste-5.png}

@@

@@

\end{minipage}%
\newline
\begin{minipage}[t]{\linewidth}

\raisebox{-\height}{

\includegraphics{images/paste-6.png}

@@

\end{minipage}%

\caption{\label{fig-route-types}Illustration of the Fastest and Quietest
route networks for central and East Limmerick.}
